\documentclass{article}

% Replace with the real NeurIPS style file before submission:
% \usepackage[final]{neurips_2024}
\usepackage[margin=1in]{geometry}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{url}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{nicefrac}
\usepackage{microtype}
\usepackage{graphicx}

\title{Credit Card Fraud Detection with Benford's Law\\and Sequence-Inspired Features}

\author{%
  Dutch Casa\\
  Auburn University\\
  \texttt{email@auburn.edu}\\
}

\begin{document}

\maketitle

\begin{abstract}
TODO.
\end{abstract}

\section{Introduction}
TODO. Problem statement, motivation, scope, SMART objectives.

\section{Related Work}
TODO. Stripe's Payments Foundation Model and card-testing detection. Benford's Law in forensic accounting. Classical fraud detection baselines on the ULB dataset.

\section{Data}
TODO. ULB dataset description. Class imbalance. Time-ordered evaluation rationale.

\section{Methods}
\subsection{Baselines}
TODO.
\subsection{Benford's Law Features}
TODO.
\subsection{Time-Window Aggregates}
TODO.
\subsection{Gradient-Boosted Trees}
TODO.
\subsection{Neural Models}
TODO.

\section{Experiments}
TODO. Hyperparameter search, validation strategy, metrics.

\section{Results}
TODO. Per-model table. PR curves. Error analysis.

\section{Discussion}
TODO. Where each approach helps. Benford's contribution.

\section{Limitations}
TODO. Anonymized features, single-dataset evaluation, synthetic time ordering concerns.

\section{Conclusion}
TODO.

\bibliographystyle{plain}
\begin{thebibliography}{9}
\bibitem{dalpozzolo2018}
Dal Pozzolo, A., Boracchi, G., Caelen, O., Alippi, C., and Bontempi, G.
\textit{Credit card fraud detection: a realistic modeling and a novel learning strategy.}
IEEE Transactions on Neural Networks and Learning Systems, 2018.

\bibitem{stripeflywheel2024}
Stripe Engineering.
\textit{The ML flywheel: How we continually improve our models to reduce card testing.}
\url{https://stripe.com/blog/the-ml-flywheel-how-we-continually-improve-our-models-to-reduce-card-testing}, 2024.

\bibitem{benford1938}
Benford, F.
\textit{The law of anomalous numbers.}
Proceedings of the American Philosophical Society, 78(4):551--572, 1938.

\bibitem{nigrini2012}
Nigrini, M. J.
\textit{Benford's Law: Applications for Forensic Accounting, Auditing, and Fraud Detection.}
Wiley, 2012.

\end{thebibliography}

\end{document}
